Adaptive Hierarchical Sliding Mode Control with Input Saturation for Attitude Regulation of Multi-satellite Tethered System

### 2016-07-15 manuscript.tex
20160715

where $J_1$ denotes the moment of inertia of the satellite array for the vertical axis; $J_1=3I_1+2ml^2$ in which $I_1$ refers to the moment of inertia of an individual participant in the three-body inline frame; $l$ identifies the tether length; $J_2$ has the similar expression $J_2=3I_2+2ml^2$ for the second axis. In Figure~\ref{Figure:3satellite}, the first axis is perpendicular to the rotation plane which is determined by the other two axes. Attach the third axis to the tether, and the rotation about the second axis generates the out-of-plane motion. Without loss of generality, it is quite reasonable to assume that the individual satellite is axis-symmetric thoroughly. The participating satellites arranging in a line neatly gives rise to $I_1=I_2$, and in addition the array is axis-symmetric about the third axis~\cite{chung2008propellant1}. Hence, Eq.~(\ref{eq:3body}) reduces to

@@

\end{align} \begin{color}{red}From equations above, $\omega_2$ is independent from $\omega_1$. Similar to the dynamic state $\omega_3$, dynamic state $\omega_2$ can be controlled separately without affecting the in-plane dynamics~\cite{chung2007nonlinear,chung2007nonlinear1,chung2007nonlinear3}. For each satellite, three flywheels are mounted orthogonally to regulate the attitude. The flywheel which is mounted perpendicularly to the tether, governs the dynamic state $\omega_3$, and different from the other axes, the varying $\omega_3$ will not lead to the situation described in Figure~\ref{Figure:model3body}, hence a simple linear feedback control can achieve its attitude regulation. When we attention on the in-plane dynamics, the other two flywheel torques and thruster firing handle the out-plane dynamics, which can guarantee that the in-plane motion occurs without other disturbance from the other axes.\end{color} On the premise of the assumption that the out-of-plane plant is stable independently, the in-plane attitude dynamics, accordingly, can be described as a model consisting of three flywheels assembly and two tethers, as seen in Figure~\ref{Figure:model3body}. \begin{color}{red}The mathematical model expressed by using Euler-Lagrange equations is established, and the origin of the array is the satellite's geometrical center as well the mass center.\end{color} In the 2D plane, the three-body satellite array arranges along $X$-axis direction, and the positive directions of $\theta_i$ and $\phi_i$ are anticlockwise. $F_i$ denotes the $i$th thruster's linear force, and $u_i$ is defined to be the $i$th flywheel torque acting on the center of mass. $\Psi$ identifies the rotation angle, then the dynamic equation follows~\cite{chung2007nonlinear1}

@@

Using a simple exponential stabilization controller represses the behaviors of $\Psi$ ($\Psi\approx\theta_i$, $\ddot\Psi\rightarrow 0$) in Eq.~(\ref{eq:3bodymodel}), and the reduced dynamic equations may be derived as~\cite{chung2007nonlinear,huang2015nonlinear}:

@@

Figure~\ref{Figure:modelsinglebody} shows an individual participating satellite which rotates about the center of the array frame. \begin{color}{red}Body coordinate system $x$-$y$ requires that y axis points to the direction of the increase of the array rotation angle, and meanwhile $x$-axis is along the tether\end{color}. Assume that the tether is massless and inextensible so that the vibration dynamics can be regardless. The Kevlar physical property makes the tether strong and thin enough, i.e., SPECS owns the tether consisting of four tethers lines, and the total mass is approximate to 30 \textit{kg} for 1-km-long ribbon tether\cite{chung2007nonlinear1}. \begin{color}{red}The three-satellite inline tethered frame is assumed to rotate at a specific angular rate so that the tether keeps taut and straight at all times. In reality, the satellite will hit the tether when attitude angle $\phi_i$ crosses $\pi/2$ rad, and due to the rotation dynamics of the array and the small initial condition of $\phi_i$, we can assume that $\vert \phi\vert\le \pi/2$~\cite{chung2007nonlinear1}.\end{color}  Since the tether speed can be easily controlled by programmed tether motor and doesn't disturb any other system states, it's assumed that the tether length speed $\dot l$ is naught. Finally, assume the three-satellite inline tethered frame is manoeuvred to orbit in the second Lagrangian point of the earth-sun system referring to the SPECS project, and hence the gravity term is approximate to zero~\cite{lorenzini2006far}.\par

@@

To our knowledge, flywheels are applied as the proper actuators frequently in the attitude regulation of the satellite, for instance, the system of the SPECS project is manoeuvred by using the flywheel control strategy in most of the time~\cite{chung2008propellant1}. In the view of the mechanical structure, there are two categories of flywheels, namely, the bias moment and the zero moment. Functionally, the rotation rate of the bias moment wheels is nonnegative; the zeros moment ones can change the rotation direction. The zero moment wheels are typically known as reaction wheels, which may always maintain the whole satellite's moment zero, and are used more widely than the bias ones in the attitude regulation of the satellite. Considering the energy consumption of the system in practice, \begin{color}{red}flywheels are driven by the electricity which may be provided by energy harvesting system\end{color}, and in contrast with the thruster, the utilization of flywheels avoids consuming the limited quantities of fuel during the attitude regulation. In the aspect of regulating accuracy, the TSS need reaction wheels to generate the continuous high precise torque for the regulation in orbit, whereas thrusters consume expensive fuel to supply the linear torque output in pulse method. In addition, the reaction wheel is also convenient to equip, \begin{color}{red}and there always exists an incline reaction wheel equipped as the redundancy actuator.\end{color} For the attitude regulation, with neglecting the thruster force input, the reaction wheel control strategy changes the three-satellite inline frame into an underactuated system. More notably, the effect of the input for the control system is saturated, since the torque of an reaction wheel is not infinite. Normally, for a reaction wheel, the positive and negative torques are identical, which can be expressed by the saturation function.

@@

According to Lemma~\ref{theorem:syn}, Eq.~(\ref{eq:3bodyreduce}) indicates that the formulation of two sub-systems meets the contracting requirement, hence $(\theta_1,\phi_1)^T$ and $(\theta_1,\phi_2)^T$ will coverage to each other if an individual control law is designed to guarantee the stability of the each one~\cite{huang2015nonlinear}.\par

@@

As $M_1(\phi)$ is invertible, select state variable $x_1=\theta$, $x_2=\dot\theta$, $x_3=\phi$, $x_4=\dot\phi$ to get the following state space equations, which express the attitude dynamics of the individual participating satellite shown in Figure~\ref{Figure:modelsinglebody}:

@@

In the symbol system of the control system, the time variable is usually abbreviated if it won't lead to confusing, i.e., $S(t)$ may be simplified as $S$. HSM structures the first-level sliding surfaces as follows:

@@

Considering a sort of underactuated systems which own a stabel equilibrium point, propose the sliding surfaces as Eq.~(\ref{eq:s1s2}) and Eq.~(\ref{eq:S}), and there is a approach to guaranteeing the asymptotically convergence of the second-level sliding mode. If $s_1\in L_\infty$, $\dot s_1\in L_\infty$, the first-level sliding mode also asymptotically converges.\label{lm:1}

@@

$d_1(X,t)$ and $d_2(X,t)$ are the uncertain parts of system~(\ref{eq:model}), and satisfies the following relation $max(\vert d_1(X,t)\vert,\vert d_2(X,t)\vert) \le \zeta <\infty$, \begin{color}{red}where $\zeta$ is constant positive.\end{color}\label{as:2}

@@

Modified hierarchical sliding mode control (MHSM) constructs the first- and second-level surfaces like Eq.~(\ref{eq:s1s2}) and Eq.~(\ref{eq:S}), and thanks to the Lemma~\ref{lm:1} and Assumption~\ref{as:2}, we propose the adaptive control input as follows:

@@

For voiding the singularity of the input~(\ref{eq:u}), the selection of $\alpha$ and $\beta$ may satisfy the condition: $0<\alpha\le\beta$ with $\vert x_3\vert\le\pi/2$.

@@

Compared to the issue about stabilization of the three-satellite inline array, the central satellite is absent in the two-satellite system so that the individual torque acting on one participant will effect the other one~\cite{chung2007nonlinear}. With model reduction techniques failing in this model, the systemical simplification is unable to be achieved due to the fact that the physical construction of the satellite is almost identical. \begin{color}{red}The same mechanical structure of the satellite results in that the system do not satisfy the condition of station keeping like the simple mother satellite and sub-satellite tethered system.\end{color} In the mother satellite and sub-satellite tethered system, it requires the mass of mother satellite to be much larger than the other one, and this premise of assumption is usually met in the deployment mission of the tethered satellite system. Without any simplification, the number of the input in Eq.~(\ref{eq:2body}) is less than the degree of freedom (DOF), and meanwhile the input is coupled as well. For the reason of generality, \begin{color}{red}the condition of the actuator is similar to that in the three-satellite inline array. On the basis of the previous results, the two-satellite inline system is the underactuated system with input saturation.\end{color}\par
The solution for the attitude stability of the three-satellite inline array is valid for the two-satellite inline system. For the sake of the adaptive controller design, the system can be rewritten as the expression of Eq.~(\ref{eq:model}). Select state variables $x_1=\theta$, $x_2=\dot\theta$, $x_3=\phi_1$, $x_4=\dot\phi_1$, $x_5=\phi_2$, $x_6=\dot\phi_2$ to get the following state space equations:

@@

where $X = (x_1,x_2,x_3,x_4,x_5,x_6)^T$. \begin{color}{red}In addition, $\bar{sat}()$, $f_i(X,t)$ and $d_i(X,t)$ have the similar mathematical featureS which are illustrated in the individual system of three-satellite inline array in Eq.~(\ref{eq:model}),\end{color} and $f_i(X,t)$ and $b_i(X,t)$ can be derived:

@@

For applying the MHSM control to the attitude regulation of the two-satellite inline system shown in Eq.~(\ref{eq:2model}), the first-level iedal sliding surfaces are selected firstly as follows:

@@

Some essential results are given in advance so that the adaptive control design for the system~(\ref{eq:2model}) can be illustrated explicitly. The spatial perturbation term, $d_i(X,t)$, owns the characteristics of trigonometric function, and those bound value can be determined easily. More notably, the terms in the attitude dynamics of the two-satellite system~(\ref{eq:2body}) are a group of constant and trigonometrical terms, and furthermore, their operations are additive and multiplicative. Hence the boundary exists and can be calculated. In the regulation, the attitude angle is limited in a practical meaningful range $\vert \phi_i\vert\le\pi/2$~\cite{chung2008propellant2}. Therefore, some symbols are introduced to express the mentioned relationship, and they will take part in the design of the adaptive control in the following form:\label{rem:2}

@@

For voiding the singularity of the input, the parameter $\bar\alpha$, $\bar\beta$ and $\bar\iota$ should satisfy the the condition $0<\bar\alpha\le\bar\iota$ and $0<\bar\alpha\le\bar\beta$.\par

@@

    In addition, it is obvious that $b_5(X,t)>0$, and hence, for voiding the singularity of $\bar\alpha b_1(X,t) + \bar\beta b_3(X,t) + \bar\iota b_5(X,t)$,  the parameters should satisfy the condition $0<\bar\alpha\le\bar\beta$ and $\bar\iota>0$. $\bar\alpha b_2(X,t) + \bar\beta b_4(X,t) + \bar\iota b_6(X,t)>0$ can be obtained under the condition: $0<\bar\alpha\le\bar\iota$ and $\bar\beta>0$. Conclusively, $0<\bar\alpha\le\bar\iota$ and $0<\bar\alpha\le\bar\beta$ guarantee the non-singularity of the input in the MHSM control.

@@

@@

Referring to the experiment of SPHERES project, the simulation parameters describing the physical characteristics of the satellite are listed in Table~\ref{tab:1}. According to the parameter list, the input boundary is determined as $T_p = -T_n = 0.207Nm$. In particular the controller's output is programmed to satisfy the restriction of the actuator, which can avoid the block of the flywheels in some extent. The length of the tether is constant, since the variety of the length rate leads to an extremely complicated and unstable multi-satellite tethered systems. The reasonable length of the tether is essential, $l = 0.9m$, although the length will not take an important role in the following process of validating. In this simulation, it is assumed that the satellites expose itself to the real space environment, and there exist the solar radiation pressure torque and aerodynamic torque effecting its attitude stability. \begin{color}{red}Without loss of generality, the perturbation term is thought to be a periodic function, and the period is $5000s$ approximately, which equals to the orbital period~\cite{inamori2015magnetic,liu2013calculation}. Hence for verifying the effectiveness of the MHSM control, the satellite is exerted by a sinusoidal perturbation whose amplitude is no more than $1\times 10^{-5}Nm$ with $2\times 10^{-4}Hz$. Since the relative distance among the participating satellites is not large, without loss of generality, the form of preceding perturbation is identical.

@@

\begin{color}{red}In order to apply the MHSM scheme proposed in Section~\ref{sec:SMC},\end{color} the parameters of the controller is exhibited, $c_1 = 10$ and $c_2 = 3$, which meet the demand of Eq.~(\ref{eq:s1s2}), the parameters of second-level sliding surface in Eq.~(\ref{eq:S}), $\alpha=\beta=1$. The adaptive parameters can be decided as follows: $\delta = 1.8$, $\eta(0) = 1e^{-4}$, $\zeta = 1$ and $\gamma = 1\times 10^{-4}$. $\rho$ obtained due to the simulation process, which satisfies the conditions of Lyapunov stability.\par

@@

Use MHSM scheme to regulate the individual system shown as Eq.~(\ref{eq:individualsys}), and the guidance situation of sliding mode is illustrated in Figure~\ref{Figure:sm} where $s_1$ and $s_2$ converge to origins as well as $S$. It is the trajectory of $s_1$ that nearly overlaps with the one of $S$, and $s_2$ fluctuates slightly in the vicinity of the origin. Paying attention on the convergence of each sliding mode, it is obvious that $S$, $s_1$ and $s_2$ reach the neighbour region of the origin at about 1.2 $s$ and stay stable. Incidentally, the state of the angle and the torque are both physical meaningful.\par
The situation of the attitude regulation is illustrated in Figure~\ref{Figure:attitude}, in which the array angular rate is adjusted to be the desired value from the initial condition so that the individual satellites and the central satellite are rotating together at the same velocity. It is at about 1.2 $s$ when the trajectory of the attitude angle converges to the preset value, $\phi_d = 0$, so does the array angular rate. \begin{color}{red}The performance of the decentralized control reported in~\cite{chung2008propellant1} is also illustrated in Figure~\ref{Figure:attitude}. In~\cite{chung2008propellant1}, a pair of thrusters are used to dump the angular momentum caused by the saturation of the flywheel speed, and for reducing the consumption of thruster firing, a little gain design is demanded in the decentralized control strategy. Hence, the decentralized control inevitably leads to a slow smooth attitude regulation shown in Figure~\ref{Figure:attitude}. Compared with the the decentralized control scheme, one can find that the MHSM control demonstrates a fast regulation, and although the amplitudes of the varying attitude angle and the array angular rate of the MHSM control are greater with the variations falling in $[-0.05,0.2]$ $rad$ and $[0.225,0.375]$ $rad/s$, respectively, this variations are tolerable in some fast attitude scenarios of the TSS~\cite{Williams2009745}. Even if the input saturation occurs during the attitude regulation, the MHSM control scheme guarantees the stability of the system, and hence the selection of the gain is flexible so that the performance of the control system can be adjusted by the suitable parameters. \end{color}\par
The characteristics of the input saturation are exhibited in Figure~\ref{Figure:Torque}, and the existence of the input bound makes the curves not smooth any more. In particular, \begin{color}{red}it cuts off the oversize input signal to be a bound value, and the input resumes to be regular once the control signal is located in the region $[T_n,T_p]$.\end{color} The boundary of the input is decided by the physical property of the flywheel equipped in the satellite, and the bound value is $0.207Nm$ bidirectionally in this section. In Figure~\ref{Figure:Torque}, the saturation occurs from about $0s$ to $0.6s$, which is zoomed out for examining more details, and the torque keeps a low-amplitude fluctuation in the neighbour region of the origin after 1.2 $s$. That means that the torque utilized to make the system stable, still performs accurately, although the stability of the attitude dynamics for the individual satellite has achieved macroscopically. It is also easy to find that the perturbations don't introduce distinct contaminations into the control system, in another word, the anti-interference ability of the proposed scheme is excellent.

@@

The parameter set of the MHSM scheme is given firstly for stabilizing the attitude of the two-satellite system expressed in Eq.~(\ref{eq:2model}) in Section~~\ref{sec:SMC2}. The set of the parameters for first-level sliding surface design, $\bar c_1 = 5$, $\bar c_2 =3$ and $\bar c_3=1$, satisfies the positive requirement, and meanwhile, for the the second-level sliding surface design $\bar\alpha$$=\bar\beta=\bar\iota=1$ will not effect the performance of the control system in some extent. List adaptive parameters as follows: $\bar\delta = 2.1$, $\bar\eta(0)=5\times 10^{-4}$, $\bar\gamma = 1\times 10^{-4}$ and $\bar\varpi = 2$. In addition, $\bar\xi,\bar\rho$ can be obtained due to the simulation process. All mentioned parameters guarantee Lyapunov stability of the system dynamics.\par

@@

In this part, the system is fixed-point rotating at the desired angular rate $\dot\theta_d = 0.25$, while the tether keeps stiff. In the final stage, $\phi_{i}$, the attitude angle, should be regulated to be 0.  Initially, the system rotates at the angular rate $\dot\theta_0=0.25$, and the attitude can be described by $\phi_{10}=0.4$ and $\phi_{20}=0.1$.\par

@@

This paper proposes a torque control scheme to adjust the attitude of the multi-satellite array system. In particular, the proposed approach accounts for two meaningful issues in practical implementation. The first issue is that the attitude dynamics of the multi-satellite array system is coupled and underactuated during the regulation process. The second one is that the actuators are usually saturated or bounded in the realistic application. For solving underactuated problems, the adaptive rate and the HSM control law are synthesized to obtain the MHSM control scheme, and it also takes into consideration the input saturation. The adaptive rate term is designed to compensate the impact of the saturated input so that the Lyapunov stability of the attitude dynamics can be obtained. Theoretical analysis is demonstrated to guarantee that the sliding mode dynamics reaches the ideal sliding surface. The simulation results indicate that the attitude regulation for the tethered satellite system with the control scheme effectively and efficiently.

>>>>

where $J_1$ denotes the moment of inertia of the satellite array for the vertical axis; $J_1=3I_1+2ml^2$ in which $I_1$ refers to the moment of inertia of an individual participant in the three-body inline frame; $l$ identifies the tether length; $J_2$ has the similar expression $J_2=3I_2+2ml^2$ for the second axis. In Figure~\ref{Figure:3satellite}, the first axis is perpendicular to the rotation plane which is determined by the other two axes. Attach the third axis to the tether, and the rotation about the second axis generates the out-of-plane motion. Without loss of generality, it is quite reasonable to assume that the individual satellite is axis-symmetric thoroughly. The participating satellites arranging in a line neatly gives rise to $I_1=I_2$, and in addition, the array is axis-symmetric about the third axis~\cite{chung2008propellant1}. Hence, Eq.~(\ref{eq:3body}) reduces to

@@

\end{align} \begin{color}{red}From equations above, $\omega_2$ is independent from $\omega_1$. Similar to the dynamic state $\omega_3$, dynamic state $\omega_2$ can be controlled separately without affecting the in-plane dynamics~\cite{chung2007nonlinear,chung2007nonlinear1,chung2007nonlinear3}. For each satellite, three flywheels are mounted orthogonally to regulate the attitude. The flywheel which is mounted perpendicularly to the tether, governs the dynamic state $\omega_3$, and different from the other axes, the varying $\omega_3$ will not lead to the situation described in Figure~\ref{Figure:model3body}, hence a simple linear feedback control can achieve its attitude regulation. When we attention on the in-plane dynamics, the other two flywheel torques and thruster firing handle the out-plane dynamics, which can guarantee that the in-plane motion occurs without the disturbance from the other axes.\end{color} On the premise of the assumption that the out-of-plane plant is stable independently, the in-plane attitude dynamics, accordingly, can be described as a model consisting of three flywheels assembly and two tethers, as seen in Figure~\ref{Figure:model3body}. \begin{color}{red}The mathematical model expressed by using Euler-Lagrange equations is established, and the origin of the array is the satellite's geometrical center.\end{color} In the 2D plane, the three-body satellite array arranges along $X$-axis direction, and the positive directions of $\theta_i$ and $\phi_i$ are anticlockwise. $F_i$ denotes the $i$th thruster's linear force, and $u_i$ is defined to be the $i$th flywheel torque acting on the center of mass. $\Psi$ identifies the rotation angle, then the dynamic equation follows~\cite{chung2007nonlinear1}

@@

Using a simple exponential stabilization controller represses the behaviors of $\Psi$ ($\Psi\approx\theta_i$, $\ddot\Psi\rightarrow 0$) in Eq.~(\ref{eq:3bodymodel}), and the reduced dynamic equations can be derived as~\cite{chung2007nonlinear,huang2015nonlinear}:

@@

Figure~\ref{Figure:modelsinglebody} shows an individual participating satellite which rotates about the center of the array frame. \begin{color}{red}Body coordinate system $x$-$y$ requires that y axis points to the direction of the increasing array rotation angle, while $x$-axis is along the tether\end{color}. Assume that the tether is massless and inextensible so that the vibration dynamics can be regardless. The Kevlar physical property makes the tether strong and thin enough, i.e., SPECS owns the tether consisting of four tethers lines, and the total mass is approximate to 30 \textit{kg} for 1-km-long ribbon tether\cite{chung2007nonlinear1}. \begin{color}{red}The three-satellite inline tethered frame is assumed to rotate at a specific angular rate so that the tether keeps taut and straight at all times. In reality, the satellite will hit the tether when attitude angle $\phi_i$ crosses $\pi/2$ rad, and due to the rotation dynamics of the array and the small initial condition of $\phi_i$, we can assume that $\vert \phi\vert\le \pi/2$~\cite{chung2007nonlinear1}.\end{color}  Since the tether speed can be easily controlled by programmed tether motor and doesn't disturb any other system states, it's assumed that the tether length speed $\dot l$ is naught. Finally, assume the three-satellite inline tethered frame is manoeuvred to orbit in the second Lagrangian point of the earth-sun system referring to the SPECS project, and hence the gravity term is approximate to zero~\cite{lorenzini2006far}.\par

@@

To our knowledge, flywheels are frequently applied as the proper actuators in the attitude regulation of the satellite, for instance, the system of the SPECS project is manoeuvred by using the flywheel control strategy most of the time~\cite{chung2008propellant1}. In the view of the mechanical structure, there are two categories of flywheels, namely, the bias moment and the zero moment. Functionally, the rotation rate of the bias moment wheels is nonnegative, while the zeros moment ones can change the rotation direction. The zero moment wheels are typically known as reaction wheels, which may always maintain the whole satellite's moment zero, and are used more widely than the bias ones in the attitude regulation of the satellite. Considering the energy consumption of the system in practice, \begin{color}{red}flywheels are driven by the electricity which may be provided by energy harvesting system\end{color}, and in contrast with the thruster, the utilization of flywheels avoids consuming the limited quantities of fuel during the attitude regulation. In the aspect of regulating accuracy, the TSS need reaction wheels to generate the continuous high precise torque for the regulation in orbit, whereas thrusters consume expensive fuel to supply the linear torque output in pulse method. In addition, the reaction wheel is also convenient to equip, \begin{color}{red}and furthermore there always exists an incline reaction wheel equipped as the redundancy actuator.\end{color} For the attitude regulation, with the thruster force input neglected, the reaction wheel control strategy changes the three-satellite inline frame into an underactuated system. More notably, the effect of the input for the control system is saturated, since the torque of an reaction wheel is not infinite. Normally, for a reaction wheel, the positive and negative torques are identical, which can be expressed by the saturation function.

@@

According to Lemma~\ref{theorem:syn}, Eq.~(\ref{eq:3bodyreduce}) indicates that the formulation of two sub-systems meets the contracting requirement, hence $(\theta_1,\phi_1)^T$ and $(\theta_1,\phi_2)^T$ will converge to each other if an individual control law is designed to guarantee the stability of the each one~\cite{huang2015nonlinear}.\par

@@

As $M_1(\phi)$ is invertible, select state variable $x_1=\theta$, $x_2=\dot\theta$, $x_3=\phi$, $x_4=\dot\phi$ to get the following state space equations, which expresses the attitude dynamics of the individual participating satellite shown in Figure~\ref{Figure:modelsinglebody}:

@@

In the symbol system of the control system, the time variable is usually abbreviated if it won't lead to confusing, i.e., $S(t)$ may be simplified as $S$. The HSM control scheme structures the first-level sliding surfaces as follows:

@@

Considering a sort of underactuated system which owns a stable equilibrium point, propose the sliding surfaces as Eq.~(\ref{eq:s1s2}) and Eq.~(\ref{eq:S}), and there is an approach to guarantee the asymptotically convergence of the second-level sliding mode. If $s_1\in L_\infty$, $\dot s_1\in L_\infty$, the first-level sliding mode also asymptotically converges.\label{lm:1}

@@

$d_1(X,t)$ and $d_2(X,t)$ are the uncertain parts of system~(\ref{eq:model}), and satisfy the following relation $max(\vert d_1(X,t)\vert,\vert d_2(X,t)\vert) \le \zeta <\infty$, \begin{color}{red}where $\zeta$ is constant positive.\end{color}\label{as:2}

@@

Modified hierarchical sliding mode control (MHSM) constructs the first-level and second-level surfaces like Eq.~(\ref{eq:s1s2}) and Eq.~(\ref{eq:S}), and thanks to the Lemma~\ref{lm:1} and Assumption~\ref{as:2}, we propose the adaptive control input as follows:

@@

For avoiding the singularity of the input~(\ref{eq:u}), the selection of $\alpha$ and $\beta$ may satisfy the condition: $0<\alpha\le\beta$ with $\vert x_3\vert\le\pi/2$.

@@

Compared to the issue about stabilization of the three-satellite inline array, the central satellite is absent in the two-satellite system so that the individual torque acting on one participant will effect the other one~\cite{chung2007nonlinear}. With model reduction techniques failing in this model, the system simplification is unable to be achieved due to the fact that the physical construction of the satellite is almost identical. \begin{color}{red}The same mechanical structure of the satellite results in that the system does not satisfy the condition of station keeping like the simple mother satellite and sub-satellite tethered system.\end{color} In the mother satellite and sub-satellite tethered system, it requires the mass of mother satellite to be much larger than the other one, and this premise of assumption is usually met in the deployment mission of the tethered satellite system. Without any simplification, the number of the input in Eq.~(\ref{eq:2body}) is less than the degree of freedom (DOF), and meanwhile the input is coupled as well. For the reason of generality, \begin{color}{red}the condition of the actuator is similar to that in the three-satellite inline array. On the basis of the previous results, the two-satellite inline system is the underactuated system with input saturation.\end{color}\par
The MHSM control scheme can also be applied to the attitude regulation of the two-satellite inline system. For the sake of the adaptive controller design, the system can be rewritten as the expression of Eq.~(\ref{eq:model}). Select state variables $x_1=\theta$, $x_2=\dot\theta$, $x_3=\phi_1$, $x_4=\dot\phi_1$, $x_5=\phi_2$, $x_6=\dot\phi_2$ to get the following state space equations:

@@

where $X = (x_1,x_2,x_3,x_4,x_5,x_6)^T$. \begin{color}{red}In addition, $\bar{sat}()$, $f_i(X,t)$ and $d_i(X,t)$ have the similar mathematical features which are illustrated in the individual system of three-satellite inline array in Eq.~(\ref{eq:model}),\end{color} and $f_i(X,t)$ and $b_i(X,t)$ can be derived:

@@

For applying the MHSM control to the attitude regulation of the two-satellite inline system shown in Eq.~(\ref{eq:2model}), the first-level ideal sliding surfaces are selected firstly as follows:

@@

Some essential results are given in advance so that the adaptive control design for the system~(\ref{eq:2model}) can be illustrated explicitly. The spatial perturbation term, $d_i(X,t)$, owns the characteristics of trigonometric function, and those bound value can be determined easily. More notably, the terms in the attitude dynamics of the two-satellite system~(\ref{eq:2body}) are a group of constants and trigonometrical terms, and furthermore, their operations are additive and multiplicative. Hence the boundary exists and can be calculated. In the regulation, the attitude angle is limited in a practically meaningful range $\vert \phi_i\vert\le\pi/2$~\cite{chung2008propellant2}. Therefore, some symbols are introduced to express the mentioned relationship, and they will take part in the design of the adaptive control in the following form:\label{rem:2}

@@

For avoiding the singularity of the input, the parameter $\bar\alpha$, $\bar\beta$ and $\bar\iota$ should satisfy the the condition $0<\bar\alpha\le\bar\iota$ and $0<\bar\alpha\le\bar\beta$.\par

@@

    In addition, it is obvious that $b_5(X,t)>0$, and hence, for avoiding the singularity of $\bar\alpha b_1(X,t) + \bar\beta b_3(X,t) + \bar\iota b_5(X,t)$,  the parameters should satisfy the condition $0<\bar\alpha\le\bar\beta$ and $\bar\iota>0$. $\bar\alpha b_2(X,t) + \bar\beta b_4(X,t) + \bar\iota b_6(X,t)>0$ can be obtained under the condition: $0<\bar\alpha\le\bar\iota$ and $\bar\beta>0$. Conclusively, $0<\bar\alpha\le\bar\iota$ and $0<\bar\alpha\le\bar\beta$ guarantee the non-singularity of the input in the MHSM control.

@@

Tether length &0.9 \textit{m}\\

@@

Referring to the experiment of SPHERES project, the simulation parameters describing the physical characteristics of the satellite are listed in Table~\ref{tab:1}. According to the parameter list, the input boundary is determined as $T_p = -T_n = 0.207Nm$. In particular the controller's output is programmed to satisfy the restriction of the actuator, which can avoid the block of the flywheels to some extent. \begin{color}{red}Based on the assumption that the tether is straight, taut and rigid during the attitude regulation, the length of the tether $l$ is constant with $\dot l =0$. In this simulation, it is assumed that the satellites are exposed to the real space environment, and there exist the solar radiation pressure torque and aerodynamic torque affecting their attitude stabilities. Without loss of generality, the perturbation term is thought to be a periodic function, and the period is $5000s$ approximately, which equals to the orbital period~\cite{inamori2015magnetic,liu2013calculation}. Hence for verifying the effectiveness of the MHSM control, the satellite is exerted by a sinusoidal perturbation whose amplitude is no more than $1\times 10^{-5}Nm$ with $2\times 10^{-4}Hz$. Since the relative distance among the participating satellites is not large, without loss of generality, the form of preceding perturbation is identical.

@@

\begin{color}{red}In order to apply the MHSM scheme proposed in Section~\ref{sec:SMC},\end{color} the parameters of the controller is exhibited, $c_1 = 10$ and $c_2 = 3$, which meet the demand of Eq.~(\ref{eq:s1s2}), and the parameters of second-level sliding surface in Eq.~(\ref{eq:S}), $\alpha=\beta=1$. The adaptive parameters can be decided as follows: $\delta = 1.8$, $\eta(0) = 1e^{-4}$, $\zeta = 1$ and $\gamma = 1\times 10^{-4}$. $\rho$ obtained from the simulation process, which satisfies the conditions of Lyapunov stability.\par

@@

Use MHSM scheme to regulate the individual system shown as Eq.~(\ref{eq:individualsys}), and the guidance situation of sliding mode is illustrated in Figure~\ref{Figure:sm} where $s_1$ and $s_2$ converge to origins as well as $S$. It is the trajectory of $s_1$ that nearly overlaps with the one of $S$, and $s_2$ fluctuates slightly in the vicinity of the origin. Paying attention to the convergence of each sliding mode, it is obvious that $S$, $s_1$ and $s_2$ reach the neighbour region of the origin at about 1.2 $s$ and stay stable. Incidentally, the state of the angle and the torque are both meaningful in practical engineering application.\par
The situation of the attitude regulation is illustrated in Figure~\ref{Figure:attitude}, in which the array angular rate is adjusted to be the desired value from the initial condition so that the individual satellites and the central satellite are rotating together at the same velocity. It is at about 1.2 $s$ when the trajectory of the attitude angle converges to the preset value, $\phi_d = 0$. \begin{color}{red}The performance of the decentralized control reported in~\cite{chung2008propellant1} is also illustrated in Figure~\ref{Figure:attitude}. In~\cite{chung2008propellant1}, a pair of thrusters are used to dump the angular momentum caused by the saturation of the flywheel speed, and for reducing the consumption of thruster firing, a little gain design is demanded in the decentralized control strategy. Hence, the decentralized control inevitably leads to a slow smooth attitude regulation shown in Figure~\ref{Figure:attitude}. Compared with the the decentralized control scheme, one can find that the MHSM control demonstrates a fast regulation, and although the amplitudes of the varying attitude angle and the array angular rate of the MHSM control are greater with the variations falling in $[-0.05,0.2]$ $rad$ and $[0.225,0.375]$ $rad/s$, respectively, this variations are tolerable in some fast attitude scenarios of the TSS~\cite{Williams2009745}. Even if the input saturation occurs during the attitude regulation, the MHSM control scheme guarantees the stability of the system, and hence the selection of the gain is flexible so that the performance of the control system can be adjusted by the suitable parameters. \end{color}\par
The characteristics of the input saturation are exhibited in Figure~\ref{Figure:Torque}, and the existence of the input bound makes the curves not smooth any more. In particular, \begin{color}{red}it cuts down the oversize input signal to a bound value, and the input resumes to be regular once the control signal is located in the region $[T_n,T_p]$.\end{color} The boundary of the input is decided by the physical property of the flywheel equipped in the satellite, and the bound value is $0.207Nm$ bidirectionally in this section. In Figure~\ref{Figure:Torque}, the saturation occurs from about $0s$ to $0.6s$, which is zoomed out for examining more details, and the torque keeps a low-amplitude fluctuation in the neighbour region of the origin after 1.2 $s$. That means that the torque utilized to make the system stable, still performs accurately, although the stability of the attitude dynamics for the individual satellite has achieved macroscopically. It is also easy to find that the perturbations don't introduce distinct contaminations into the control system, in other words, the anti-interference ability of the proposed scheme is excellent.

@@

The parameter set of the MHSM scheme is given firstly for stabilizing the attitude of the two-satellite system expressed in Eq.~(\ref{eq:2model}) in Section~~\ref{sec:SMC2}. The set of the parameters for first-level sliding surface design, $\bar c_1 = 5$, $\bar c_2 =3$ and $\bar c_3=1$, satisfies the positive requirement, and meanwhile, for the the second-level sliding surface design $\bar\alpha$$=\bar\beta=\bar\iota=1$ will not effect the performance of the control system to some extent. List adaptive parameters as follows: $\bar\delta = 2.1$, $\bar\eta(0)=5\times 10^{-4}$, $\bar\gamma = 1\times 10^{-4}$ and $\bar\varpi = 2$. In addition, $\bar\xi,\bar\rho$ can be obtained due to the simulation process. All mentioned parameters guarantee Lyapunov stability of the system dynamics.\par

@@

In this part, the system is fixed-point rotating at the desired angular rate $\dot\theta_d = 0.25$, while the tether keeps stiff. In the final stage, $\phi_{i}$, the attitude angle, should be regulated to 0.  Initially, the system rotates at the angular rate $\dot\theta_0=0.25$, and the attitude can be described by $\phi_{10}=0.4$ and $\phi_{20}=0.1$.\par

@@

This paper proposes a torque control scheme to adjust the attitude of the multi-satellite array system. In particular, the proposed approach accounts for two meaningful issues in practical implementation. The first issue is that the attitude dynamics of the multi-satellite array system is coupled and underactuated during the regulation process. The second one is that the actuators are usually saturated or bounded in the realistic application. For solving underactuated problems, the adaptive rate and the HSM control law are synthesized to obtain the MHSM control scheme, and the input saturation is also taken into consideration . The adaptive rate term is designed to compensate the impact of the saturated input so that the Lyapunov stability of the attitude dynamics can be obtained. Theoretical analysis is demonstrated to guarantee that the sliding mode dynamics reach the ideal sliding surface. \begin{color}{red}The simulation results indicate that the control scheme designed for the attitude regulation of the tethered satellite system is effectively and efficiently.\end{color}
